Time--Frequency Scattering Accurately Models Auditory Similarities Between Instrumental Playing Techniques

### 2020-11-02 paper/paper.tex
add use case subsection
write on personalization in use case

Behind the overarching challenge of coming up with a robust predictive model for listening behaviors in humans, the main practical application of timbre similarity retrieval lies in the emerging topic of computer-assisted orchestration \cite{maresz2013cmr}.
In such context, the composer queries the software with an arbitrary audio signal.
The outcome is another audio signal which is selected from a database of instrumental samples and perceptually similar to the query.
The advantage of this search is that, unlike the query, the retrieved sound is precisely encoded in terms of duration, pitch, intensity, instrument, and playing technique.
Thus, following the aesthetic tradition of spectralism in contemporary music creation, the computer serves as a bridge from the auditory level to the symbolic level, \ie{} from a potentially infinite realm of timbral sensations to a musical score of predefined range \cite{caetano2019swarm}.

@@

Composers may personalize their search engine $\mathbf{\Phi}$ by manually defining a cluster graph via the Cyberlioz interface (see \lnameref{sec:data-collection} section).
This preliminary annotation lasts $30$ to $60$ minutes, which is relatively short in comparison with the duration of the $N^\prime = 9346$ audio samples in $\mathcal{G}_k$ after extension to all available pitches and dynamics: i.e., roughly three hours of audio.

>>>>

\subsection*{Use case}

Behind the overarching challenge of coming up with a robust predictive model for listening behaviors in humans, the main practical application of timbre similarity retrieval lies in the emerging topic of computer-assisted orchestration \cite{maresz2013cmr}.
In such context, the composer queries the software with an arbitrary audio signal.
The outcome is another audio signal which is selected from a database of instrumental samples and perceptually similar to the query.

The advantage of this search is that, unlike the query, the retrieved sound is precisely encoded in terms of duration, pitch, intensity, instrument, and playing technique.
Thus, following the aesthetic tradition of spectralism in contemporary music creation, the computer serves as a bridge from the auditory level to the symbolic level, \ie{} from a potentially infinite realm of timbral sensations to a musical score of predefined range \cite{caetano2019swarm}.

Composers may personalize their search engine by manually defining a cluster graph via the Cyberlioz interface (see \lnameref{sec:data-collection} section).
This preliminary annotation lasts $30$ to $60$ minutes, which is relatively short in comparison with the duration of the $N^\prime = 9346$ audio samples in the database: i.e., roughly three hours of audio.

@@
